% Don't like 10pt? Try 11pt or 12pt
\documentclass[11pt]{article}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}
\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[T1]{fontenc}
\usepackage{etaremune}

% Simpler bibsection for CV sections
% (thanks to natbib for inspiration)
\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}
    {\minipage[t]{\linewidth}\list{}{%
        \setlength{\leftmargin}{\bibhang}%
        \setlength{\itemindent}{-\leftmargin}%
        \setlength{\itemsep}{\bibsep}%
        \setlength{\parsep}{\z@}%
        }}
    {\endlist\endminipage}
\makeatother


\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=0.025in,     % Length of section titles
            marginparsep=.03in,       % Space between titles and text
            margin=0.6in, %45in,               % 1 inch margins
            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}


\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{black}{rgb}{0,0,0}
\hypersetup{colorlinks,breaklinks,
            linkcolor= black,urlcolor= black,
            anchorcolor= black,citecolor= black}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\begin{center} \LARGE \bfseries\textsc{ #1} \end{center}}%[-0.15\baselineskip]%
                 %\rule{\columnwidth}{1pt}%
        \end{minipage}}

\newcommand{\address}[4]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
         {\begin{center} \vspace{0.25cm} \textnormal \bfseries #1 \\ #2 ~~ #4 ~~ #3 \end{center}}%[-0.15\baselineskip]%
                 %\rule{\columnwidth}{1pt}%
        \end{minipage}}


\newenvironment{heading}[1]{\hspace{0.5cm} \textbf{#1}}

\newenvironment{headingtitle}[2]{\hspace{0.5cm} \textbf{#1}, #2}

\newenvironment{dateheadingtitle}[2]{ #1 #2.}

\newenvironment{locationdate}[2]{#2 \quad \textbf{#1}.}

\newenvironment{positionlocationdate}[3]{#3 \quad \textbf{#1, #2}.}

\newenvironment{supervision}[3]{#3 \quad \textbf{#1} #2.}

\definecolor{dark-gray}{gray}{0.1}

\newenvironment{sectionheader}[1]{\vspace{0.5cm}\color{black}{\large{\bfseries{\textsc{#1}}}\normalsize
}\color{Black}}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]
        {\begin{itemize}[ #1]}{\end{itemize}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]
        {\begin{compactitem}[#1]}{\end{compactitem}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{Simon Wolfgang Funke}
\address{Simula Research Laboratory, Martin Linges vei 17, 1364 Fornebu, Norway}{simon@simula.no}{+47 40 62 55 86}{\href{http://www.simonfunke.com}{simonfunke.com}}

\newlength{\rcollength}\setlength{\rcollength}{1.0in}%

%%%%%%%%%%%%%%%%%%%%%%%%%% Personal information %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionheader{Personal information}

\begin{itemize}
%\item[] Name: Funke, Simon Wolfgang
    \vspace{-0.2cm}
\item[] Date of birth: 17.10.1983
    \vspace{-0.2cm}
\item[] Sex: Male
    \vspace{-0.2cm}
\item[] Nationality: German
    \vspace{-0.2cm}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%% Employment %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionheader{Positions}
\begin{outerlist}
\item[] \positionlocationdate{\hspace{-0.2cm}Research Director}{Simula Research Laboratory, Oslo, Norway}{2019 - today}
\item[] \positionlocationdate{\hspace{-0.2cm}Senior Research Scientist}{Simula Research Laboratory, Oslo, Norway}{2015 - today}
\item[] \positionlocationdate{\hspace{-0.2cm}Head of Department}{Simula Research Laboratory, Oslo, Norway}{2018 - 2019}
%\item[] \positionlocationdate{\hspace{-0.2cm}Senior Research Scientist}{Simula Research Laboratory, Oslo, Norway}{2016 - today}
%\item[] \positionlocationdate{\hspace{-0.2cm}Research Scientist}{Simula Research Laboratory, Oslo, Norway}{2016 - today}
%\item[] \positionlocationdate{\hspace{-0.2cm}MC Member}{COST Action TD1307 (European Model Reduction Network)}{2016 - today}
\item[] \positionlocationdate{\hspace{-0.2cm}Adjoint Associate Professor}{University of Oslo, Norway}{2015 - 2017}
\item[] \positionlocationdate{\hspace{-0.2cm}Postdoctoral Fellow}{Simula Research Laboratory, Oslo, Norway}{2013 - 2015}\\
    In addition, a 20\% adjoint PostDoc position in 2014 at Imperial College London, UK.
    %Studying predictive modeling in physiological flow.
\item[] \locationdate{Consultant, Kalkulo AS, Oslo, Norway}{2014 - 2015}
        %Metocean model for oil\&gas industry company.
\item[] \locationdate{Consultant, E.ON AG, D\"usseldorf, Germany}{2013 - 2014}
\item[] \positionlocationdate{\hspace{-0.2cm}CTO}{RedHotRails LLP, UK}{2011 - today}
        %Numerical study of safety measures for the release of toxic dusts.
%\item[] \locationdate{MeyGen }{2013 - 2014}
        %Helped to improve the tidal turbine layouts
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%% Employment %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Funding:
%Call: Open Disruptive Innovation Scheme (implemented through the SME instrument)
%Position: Lead Developer and CTO
%Duration: 6 months (from December 2015 - May 2016)
%Amount: € 50.000

%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionheader{Education}

\begin{outerlist}
\item[] \positionlocationdate{PhD, Computational science}{Imperial College London, UK}{2009 - 2013}
        \begin{innerlist}
            \item Thesis title: \textit{The automation of PDE-constrained optimisation and its applications}.
            \item Department of Earth Science and Engineering.
            \item Supervisors: M.D. Piggott, P.E. Farrell, P.A. Allison, G.J. Gorman.
            \item Date of approved disputation: 01.03.2013.
        \end{innerlist}
\item[] \positionlocationdate{Erasmus}{\'Ecole normale sup\'erieure de Lyon, France}{2007}
\item[] \positionlocationdate{Diplom, Mathematics}{Technische Universit\"at M\"unchen, Germany}{2004 - 2009}
            \begin{innerlist}
                \item Passed with high distinction (1.0).
                \item Thesis title: \textit{Fast solvers for the Navier-Stokes equations on high Reynold numbers}.
                \item Department of Mathematics.
                \item The German Diplom is equivalent to a Master degree.
                \item Supervisor: M. Ulbrich.
            \end{innerlist}
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%% Awards %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionheader{Awards and Prizes}
\begin{itemize}
\item {\textbf{Wilkinson Prize for Numerical Software}}, 2015\\
    The Wilkinson prize for Numerical Software is a prestigous prize in scientific computing, awarded every four years to the authors of an outstanding piece of numerical software.
    In 2015, the prize was awarded to Funke and his co-authors P.E. Farrell, D.A. Ham and M.E. Rognes for the high-level AD tool dolfin-adjoint.
\item Best Poster Award, FEniCS 2017
\item Best Poster Award, CSE 2015
\item Imperial College Startup Venture Catalyst Award, 2013
\item {Google Interactivism Award}, 2011
\item {Imperial College Excellence Award}, 2010%\\
%This award was received as part of the Applied Modelling And Computation Group, Imperial College London for its high academic achievements and significant future potential.
\item {Grantham Institute for Climate Change and Fujitsu CASE Studentship}, 2009
%    This PhD studentship was received to develop novel numerical methods on renewable energy using high-performance computing.
\item Hurwitz-Association Award for an excellence diploma thesis, 2009
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%% Awards %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionheader{Funding}
\begin{itemize}
\item PI on NOK 7M FRIPRO Young Research Talent ``Simulation-based optimisation with dynamic domains'', (\#251237/F20), 2016
\item EU Horizon 2020 SME instrument, IMERSO AS, 2015
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%% Mobility %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionheader{Mobility}
\begin{outerlist}
\item[] {Studied and worked in research institutions in \textbf{Germany, France, UK and Norway} (> 6 months).}
\item[] {Shorter research visits:
    \begin{innerlist}
        \item Heidelberg Laureate Forum, Germany (2016)
        \item Texas A\&M University, USA (2015)
        \item Humboldt University of Berlin, Germany (2013)
        \item Simula Research Laboratory, Norway (2012)
        \item Isaac Newton Institute, Cambridge, UK (2012)
        \item Institut of Atmospheric Physics, Beijing, China (2011).
    \end{innerlist}
        }
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%% Supervision %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionheader{Supervision}
\begin{outerlist}
\item[] \supervision{PostDocs:}{August Johannsson (Simula)}{}
\item[] \supervision{PhD students:}{J\/orgen Dokken (Simula), Dave Culley (Imperial College, co-supervisor)}{}
\end{outerlist}

\sectionheader{Teaching activities}
\begin{outerlist}
    \item[] \supervision{Lecturer,}{INF3331/INF4331 Higher-level programming, University of Oslo, Norway}{2015 - today}
    \item[] \supervision{Python Workshop}{NTNU Trondheim (2017, 2 days)}{2017 - today}
    \item[] \supervision{FEniCS/dolfin-adjoint Workshop}{UNISA Johannesburg (2016, 1 day), Technical University of Munich (2016, 5 days), SUURPH workshop, Simula (2016, 1 day), Simula (2016, 2 days), Simula (2014, 1 day), Zhejiang University (2014, 5 days)}{2014 - today}
%    \item[] \supervision{\hspace{1.2cm}Invited lecture,}{Introduction to PDE-constrained optimisation, Zhejiang University, China (1 week)}{2014}
    \item[] \supervision{Teaching assistant}{for courses on computational science, programming and mathematics. Department of Earth Science and Engineering, Imperial College London, UK}{2010 - 2012}
\end{outerlist}

\sectionheader{Commissions of Trust}
\begin{outerlist}
\item[] \supervision{Organiser Committee}{ECCOMAS, Young Investigators Conference}{2019}
\item[] \supervision{\textbf{Examiner}}{for 2 Master projects}{2015-today}
\item [] \supervision{\textbf{Organiser}}{of a Workshop on Advanced Techniques in Biomedical Computing, \textit{Center for Biomedical Computing}}{2015}
\item [] \supervision{\textbf{Organiser}}{of a Mini-symposium on Efficient Solvers for PDE-constrained Optimization, \textit{SIAM CSE15}}{2015}
\item[] \supervision{\textbf{Advisory Board}}{IMERSO AS, Oslo, Norway}{2014 - today}
\item[] \supervision{Reviewer}{for SIAM Journal on Scientific Computing (SIAM), Computer Physics Communications (Elsevier), Energies (MDPI) and European Wave and Tidal Energy Conference Series and Geoscientific Model Development (GMD), Applied Energy}{2013 - today}
\end{outerlist}

\sectionheader{Research Interest/Research Profile }
%Provide an ‘abstract’, no more than a short paragraph, which outlines your current and
%prospective lines of research.

Funke's research interests center around optimisation problems governed by
partial differential equations, with a focus on their numerical solution. In
particular, he is interested in the automated derivation of adjoint and tangent
linear models and their use in optimal control, data inversion and design optimisation.
He is a founder of the dolfin-adjoint project, a software which automatically
derives adjoint models from complex computer models solving partial
differential equations based on a high-level symbolic problem specification
language that mimics mathematical notation.

Funke applies these advances to applications in a wide variety of different
domains including renewable energy and bioengineering. For the renewable energy
sector, he developed OpenTidalFarm, an open-source software for optimising of
tidal turbine farms, such as the optimal position of turbines within the farm.
In bioengineering, he developes data assimilation techniques for blood flow
simulations, with the aim to tune high-fidelity numerical blood flow models to
match with MRI measurements.

%%%%%%%%%%%%%%%%%%%%%%%%%% Publications %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\sectionheader{Books}
\begin{enumerate}
    \item \textit{T Schwedes, DA Ham, SW Funke,  MD Piggott.} Mesh dependence in PDE-constrained optimisation - An Application in Tidal Turbine Array Layouts, \textit{Springer Research Brief}, \href{https://www.springer.com/de/book/9783319594828}{ISBN 978-3-319-59483-5}, 2017.
\end{enumerate}

\sectionheader{Journal publications}\\
2019
\begin{etaremune}
\setcounter{enumi}{21}
  \item \textit{R Feu, SK Kramer, MD Piggott, J Hill, SW Funke.} The trade-off between tidal-turbine array yield and environmental impact: a habitat suitability modelling approach, \textit{Renewable Energy}, \href{https://doi.org/10.1016/j.renene.2019.04.141}, 2019.
  \item \textit{PE Farrell, JE Hake, SW Funke, ME Rognes.} Automated adjoints of coupled PDE-ODE systems, \textit{SIAM Journal on Scientific Computing}, \href{https://doi.org/10.1137/17M1144532}{10.1137/17M1144532}, 2019.
  \item \textit{X Lai, OM Geier, T Fleischer, \O~Garred, E Borgen, SW Funke, S Kumar, M Zucknick, ME Rognes, T Seierstad, A-L B{\o}rresen-Dale, VN Kristensen, L Engebraaten, A K{\"o}hn-Luque, A Frigessi.} Towards the personalized computer simulation of breast cancer treatment: a multi-scale pharmacokinetic and pharmacodynamic model informed by multi-source patient data, \textit{Cancer Research}, accepted, 2019.
\end{etaremune}
2018
\begin{etaremune}
\setcounter{enumi}{18}
    \item \textit{G Balaban, H Finsberg, SW Funke, TF H\r{a}land, E Hopp, J Sundnes, S Wall, ME Rognes} In vivo estimation of elastic heterogeneity in an infarcted human heart, \textit{Biomechanics and Modeling in Mechanobiology, Springer}, \href{https://doi.org/10.1007/s10237-018-1028-5}{10.1007/s10237-018-1028-5}, 2018.
    \item \textit{SW Funke, M Nordaas, \O~Evju, MS Aln{\ae}s, K-A Mardal.} Variational data assimilation for transient blood flow simulations, \textit{International Journal for Numerical Methods in Biomedical Engineering}, \href{https://doi.org/10.1002/cnm.3152}{doi:10.1002/cnm.3152}, 2018.
\end{etaremune}
2017
\begin{etaremune} 
\setcounter{enumi}{16}
    \item \textit{DM Culley, SW Funke, SC Kramer, MD Piggott.} A surrogate-model assisted approach for optimising the size of tidal turbine arrays, \textit{International Journal of Marine Energy}, \href{https://doi.org/10.1016/j.ijome.2017.05.001}{10.1016/j.ijome.2017.05.001}, 2017.
    \item \textit{RJ du Feu, SW Funke, SC Kramer, DM Culley, J Hillm BS Halperne, MD Piggott} The trade-off between tidal-turbine array yield and impact on flow: A multi-objective optimisation problem, \textit{Renewable Energy}, \href{https://doi.org/10.1016/j.renene.2017.07.081}{10.1016/j.renene.2017.07.081}, 2017.
    \item \textit{ME Rognes, PE Farrell, SW Funke, JE Hake, MMC Maleckar} cbcbeat: an adjoint-enabled framework for computational cardiac electrophysiology, \textit{The Journal of Open Source Software}, \href{http://dx.doi.org/10.21105/joss.00224}{10.21105/joss.00224}, 2017.
    \item \textit{SW Funke, PE Farrell, MD Piggott.} Reconstructing wave profiles from inundation data, \textit{Computer Methods in Applied Mechanics and Engineering}, \href{https://doi.org/10.1016/j.cma.2017.04.019}{10.1016/j.cma.2017.04.019}, 2017.
    \item \textit{MM Noack, SW Funke.} Hybrid Genetic Deflated Newton Method for Global Optimisation, \textit{Journal of Computational and Applied Mathematics}, \href{http://dx.doi.org/10.1016/j.cam.2017.04.047}{10.1016/j.cam.2017.04.047}, 2017.
    \item \textit{SD Parkinson, SW Funke, J Hill, MD Piggott, PA Allison.} Application of the adjoint approach to optimise the initial conditions of a turbidity current (AdjointTurbidity 1.0), \textit{Geoscientific Model Development (GMD)}, \href{https://dx.doi.org/10.5194/gmd-10-1051-2017}{doi:10.5194/gmd-10-1051-2017}, 2017.
\end{etaremune}
2016
\begin{etaremune}
\setcounter{enumi}{10}
    \item \textit{SW Funke, SC Kramer, MD Piggott.} Design optimisation and resource assessment for tidal-stream renewable energy farms using a new continuous turbine approach, \textit{Renewable Energy}, \href{https://dx.doi.org/10.1016/j.renene.2016.07.039}{doi:10.1016/j.renene.2016.07.039}, 2016.
    \item \textit{DM Culley, SW Funke, SC Kramer, MD Piggott.} Integration of cost modelling within the micro-siting design optimisation of tidal turbine arrays, \textit{Renewable Energy}, \href{https://doi.org/10.1016/j.renene.2015.06.013}{doi:10.1016/j.renene.2015.06.013}, 2016.
\end{etaremune}
2015
\begin{etaremune}
\setcounter{enumi}{8}
    \item \textit{S Rao , H Xue, M Bao, SW Funke.} Determining tidal turbine farm efficiency in the Western Passage using the disc actuator theory, \textit{Ocean Dynamics}, \href{https://doi.org/10.1007/s10236-015-0906-y}{doi:10.1007/s10236-015-0906-y}, 2015
\item \textit{PE Farrell, A Birkisson, SW Funke.} Deflation techniques for finding distinct solutions of nonlinear partial differential equations, \textit{SIAM Journal on Scientific Computing}, \href{https://doi.org/10.1137/140984798}{doi:10.1137/140984798}, 2015.
\item \textit{R Venell, SW Funke, S Draper, C Stevens.} Designing Large Arrays of Tidal Turbines: a synthesis and review, \textit{Renewable \& Sustainable Energy Reviews}, \href{https://doi.org/10.1016/j.rser.2014.08.022}{doi:10.1016/j.rser.2014.08.022}, 2015.
\end{etaremune}
2014
\begin{etaremune}
\setcounter{enumi}{5}
\item \textit{SW Funke, PE Farrell, MD Piggott.} Tidal turbine array optimisation using the adjoint approach, \textit{Renewable Energy}, \href{https://doi.org/10.1016/j.renene.2013.09.031}{doi:10.1016/j.renene.2013.09.031}, 2014.
\item \textit{PE Farrell, CJ Cotter, SW Funke.} A framework for the automation of generalised stability theory. \textit{SIAM Journal on     Scientific Computing}, \href{https://doi.org/10.1016/10.1137/12090074}{doi:10.1137/12090074}, 2014.
%\item \textit{PE Farrell, SW Funke}. Exploiting high-level structure in algorithmic differentiation, submitted, 2013.
\end{etaremune}
2013
\begin{etaremune}
\setcounter{enumi}{3}
\item \textit{PE Farrell, DA Ham, SW Funke, ME Rognes.} Automated derivation of the adjoint of high-level transient finite element programs, \textit{SIAM Journal on Scientific Computing}, \href{https://doi.org/10.1016/10.1137/120873558}{doi:10.1137/120873558}, 2013.
\end{etaremune}
2011
\begin{etaremune}
\item \textit{SW Funke, CC Pain, SC Kramer, MD Piggott.} A wetting and drying algorithm with a combined pressure/free-surface formulation for non-hydrostatic models, \textit{Advances in Water Resources}, \href{https://doi.org/10.1016/j.advwatres.2011.08.007}{doi:10.1016/j.advwatres.2011.08.007}, 2011.
\end{etaremune}

\sectionheader{Conference publications}
\begin{etaremune}
    \item \textit{JS Dokken, SW Funke, A Johannsson, S Schmidt.} Shape Optimization with Multiple Meshes, \textit{FEniCS 2017 Conference}, \href{https://github.com/funsim/cv/raw/master/publications/fenics_2017_proceedings.pdf}{PDF}, 2017
    \item \textit{CT Jacobs, SC Kramer, MD Piggott, SW Funke.} On the validity of tidal turbine array configurations obtained from steady-state adjoint optimisation, \textit{ECCOMAS Congress 2016}, \href{https://github.com/funsim/cv/raw/master/publications/jacobs_eccomas_2016.pdf}{PDF}, 2016.
    \item \textit{DM Culley, SW Funke, SC Kramer, MD Piggott.} Tidal stream resource assessment through optimisation of array design with quantification of uncertainty, \textit{EWTEC 2015 proceedings}, \href{https://github.com/funsim/cv/raw/master/publications/culley_ewtec_2015.pdf}{PDF}, 2015.
    \item \textit{T Roc, SW Funke, KM Thyng.} Standard methodology for tidal array project optimisation: An idealized study of the Minas Passage, \textit{EWTEC 2015 proceedings}, \href{https://github.com/funsim/cv/raw/master/publications/roc_ewtec_2015.pdf}{PDF}, 2015.
    \item \textit{SC Kramer, SW Funke, MD Piggott.} A continuous approach for the optimisation of tidal turbine farms, \textit{EWTEC 2015 proceedings}, \href{https://github.com/funsim/cv/raw/master/publications/kramer_ewtec_2015.pdf}{PDF}, 2015.
    \item \textit{DM Culley, SW Funke, SC Kramer, MD Piggott.} A hierarchy of approaches for the optimal design of tidal turbine arrays, \textit{Proceedings of the 5th International Conference on Ocean Energy}, \href{https://github.com/funsim/cv/raw/master/publications/culley_ewtec_2015.pdf}{PDF}, 2014.
\end{etaremune}

%\sectionheader{In review}
%\begin{etaremune}
%\item \textit{PE Farrell, SW Funke.} Exploiting high-level structure in algorithmic differentiation, in review, 2014.
%\item \textit{GL Barnett, SW Funke, MD Piggott.} Hybrid global-local optimisation algorithms for the layout design of tidal turbine arrays, \textit{Renewable Energy}, in review, 2014.
%\end{etaremune}

%%%%%%%%%%%%%%%%%%%%%%%%%% Dissemination %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionheader{Phd projects}

% The original thesis are published in my Simula Google drive folder under /... thesis/

\begin{outerlist}
    \item[2016-today] J\/orgen Dokken, \textit{PDE-constrained optimisation with dynamic domains}, Simula Research Laboratory
    \item[2013-2016] Dave Culley, \textit{The modelling and design optimisation of tidal stream turbine arrays}, Imperial College London
\end{outerlist}

\sectionheader{Master projects}
\begin{outerlist}
    \item[2016-2017] Andreas Thune, \textit{Parareal-based preconditioner for optimal control problems constrained by differential equations}, Simula Research Laboratory
    \item[2016-2017] Magnus Elden, \textit{Interactive visualization of scientific data using the Oculus Rift}, Simula Research Laboratory
    \item[2015-2016] Shifteh Sherafat, \textit{Model identification for remodelling blood vessels using a PDE-constrained optimisation approach}, Simula Research Laboratory
    \item[2012-2012] Kartik Upadhyaya, \textit{Numerical optimisation of tidal energy arrays in the Orkney Islands}, Imperial College London
    \item[2011-2011] Yiqun He, \textit{Suitability of 3D modelling in urban flooding}, Imperial College London
\end{outerlist}

\sectionheader{Bachelor projects}
\begin{outerlist}
    \item[2013] George Barnett, \textit{Hybrid global-local optimisation algorithms for the layout design of tidal turbine arrays}, Imperial College London
\end{outerlist}

\sectionheader{Summer/UROP projects}
\begin{outerlist}
    \item[2016] H{\aa}kon Task{\'e}n, \textit{Implementaion of dynamic turbine controls in OpenTidalFarm}, Imperical College London
    \item[2013] George Barnett, \textit{Global optimisation methods for optimising tidal turbine farms}, Imperial College London
    \item[2013] Alex Lozinski, \textit{Comparative study of the OpenTidalFarm and the MIKE ocean models}, Imperial College London
\end{outerlist}

%%%%%%%%%%%%%%%%%%%%%%%%%% Dissemination %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionheader{Dissemination}

Simon Funke attented various national and international conferences. The following list
presents a selection of presentations:
\begin{outerlist}
\item[] \textbf{Plenary lecture}, The Power of Python in Science and Education, \textit{Fysikerm{\o}te}, Troms\o, Norway, 2017 % https://docs.google.com/presentation/d/1nIpQfO2aQilM8cnhpMPtIx27IdnlXCH7RRpH-tPf6xA/edit?usp=sharing
\item[] \textbf{Best poster award}, A new algorithmic differentiation tool (not only) for FEniCS, \textit{FEniCS 2017}, LuxenBourg, Luxenbourg, 2017
\item[] Machine learning with expert systems, \textit{Simula COMMONS seminar}, Oslo, Norway, 2017
\item[] Automatic Adjoints of Multimesh Finite Element Discretisations, \textit{SIAM Conference on Computational Science \& Engineering}, Atlanta, USA, 2017
\item[] \textbf{Invited talk} Introduction to FEniCS and dolfin-adjoint, \textit{Symposium on the Application of Finite Elements in Physics and Engineering}, Johannesburg, South Africa, 2016
\item[] Designing Tidal Turbine Arrays With PDE-constrained Optimisation, \textit{ESCO2016}, Plze\v{n}, Czech Republic, 2016
\item[] \textbf{Best poster award}, dolfin-adjoint, automated adjoint models for FEniCS, \textit{SIAM Conference on Computational Science}, Salt Lake City, USA, 2015
\item[] Tidal Farm Layout Optimisation and Resource Assessment based on PDE-constrained optimisation, \textit{International Conference on Ocean Energy}, Halifax, Canada, 2014
\item[] \textbf{Invited talk}, Introduction to FEniCS and automated adjoints, \textit{Norwegian Meteorological Institute}, Oslo, Norway, 2014
%\item[] Automated adjoint models with FEniCS with applications in cardiac electrophysiology, \textit{Simula Research Laboratory}, Oslo, Norway, 2014
\item[] PDE-constrained optimisation in Hilbert spaces, \textit{FEniCS'14}, Paris, France, 2014
%\item[] Automated adjoints of finite element discretizations, \textit{SIAM Conference on Computational Science \& Engineering}, Boston, USA, 2013
%\item[] PDE-constrained optimisation using automated adjoints of finite element models, Imperial College London, London, UK, 2012
%\item[] libadjoint: a new abstraction for developing adjoint models, \textit{FEniCS'12}, Simula Research Laboratory, Oslo, Norway, 2012
%\item[] Tidal turbine optimisation using the adjoint approach, \textit{Ocean Day}, Imperial College London, London, UK, 2012
%\item[] \textbf{Invited talk}, A new way to develop discrete adjoints, Simula Research Laboratory, Oslo, Norway, 2012
%\item[] Towards a Fluidity-ICOM adjoint, \textit{International Workshop on Multiscale (Un-)structured Mesh Numerical Modelling}, Alfred Wegener Institute for Polar and Marine Research, Bremerhaven, Germany, 2011
\item[] \textbf{Invited talk} An introduction to libadjoint, Institut of Atmospheric Physics, Beijing, China, July 2011
%\item[] A wetting and drying algorithm for non-hydrostatic models with combined pressure/free-surface, \textit{European Geosciences Union General Assembly 2011}, Vienna, Austria, 2011.
%\item[] A new wetting and drying algorithm using a combined pressure/free-surface finite element method, \textit{International Workshop on Multiscale (Un)-structured Mesh Numerical Ocean Modeling}, Massachusetts Institute of Technology, Boston, USA, 2010.
\end{outerlist}

\sectionheader{Other prizes}
\begin{outerlist}
\item[] Attended the General Electrics CX hackathon as a tech-expert, London, August 2017.
\item[] Winner of BigDataHackthon for developing a machine learning algorithm that predicts the influence of people, May 2013.
\item[] Winner of the Rewired State Hack, for novel developments for a charity to improve surgical care in Africa, December 2012.
\item[] Invitation to OpenITP \& Rio de Janeiro RightsCon with the goal to develop realtime censorship detection, May 2012.
\item[] Google Interactivism Award for developing a NHS health care web application to improve waiting times in hospitals, 2012.
\item[] Winner of WaterHackathon London for developing a reporting platform for managing sanitation complaints in Tanzania. The project received media attention and was featured on the BBC, Africa, October 2011.
%\item[] Developed a SMS notification system for \url{LifeBox}{http://www.lifebox.org}
\end{outerlist}

\sectionheader{Personal development}
\begin{outerlist}
    \item[] Attended 2 day course on professional development for project leaders, 2016-2017.
\end{outerlist}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
